---
title: "edna_db"
author: "Jake Eisaguirre"
date: "2022-12-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}

# librarian downloads, if not already downloaded, and reads in needed packages
librarian::shelf(tidyverse, here, janitor, lubridate, RPostgres, rstudioapi, DBI, parsedate, stringr, hms,
                 anytime, terra, sp, rgdal, RWmisc, proj4, uuid)
```

# serdp edna data

# full serdp edna data

```{r}

full_serdp_edna <- read_csv(here("data", "serdp", "edna", "serdp_edna.csv")) %>% 
  clean_names()

```


## serdp edan site table
```{r}

serdp_site_edna <- full_serdp_edna %>%
  select(c(state, site_number, date_collected)) %>% 
  unite(site_code, state:site_number,  sep = "", na.rm = T, remove = F) %>% 
  mutate(site_code = str_to_lower(site_code),
         date_collected = format_iso_8601(parse_date(date_collected))) %>% 
  mutate(region = case_when(state == "PA" ~ "pennsylvania",
                           state == "NM" ~ "new_mexico",
                           state == "LA" ~ "louisiana",
                           state == "TN" ~ "tennessee",
                           state == "VT" ~ "vermont")) %>% 
  select(!c(state, site_number)) #%>% 
  # group_by(site_code, date_collected) %>% 
  # mutate(temp_id = cur_group_id()) %>% 
  # filter(!duplicated(temp_id)) %>% 
  # select(!c(temp_id))

codes_to_names <- read_csv(here("data", "serdp", "edna", "join_site.csv")) %>% 
  mutate(site = str_replace_all(site, " ", "_"),
         site = str_replace(site, " ", "-"))


serdp_edna_visit <- left_join(serdp_site_edna, codes_to_names, by = c("site_code")) 

serdp_edna_sitetable <- serdp_edna_visit %>% ungroup() %>% 
  group_by(site_code) %>% 
  filter(!duplicated(site_code))
  
  

```


## serdp_edna_date_table
```{r}

serdp_edna_visit_table <- serdp_edna_visit %>% 
  mutate(year = year(date_collected),
         month = month(date_collected),
         day = day(date_collected)) %>% 
  select(!c(region)) %>% 
  group_by(site, date_collected) %>% 
  mutate(temp_id = cur_group_id()) %>% 
  filter(!duplicated(temp_id)) %>% 
  select(!c(temp_id)) %>% 
  mutate(site = str_replace_all(site, "-", "_"))
  

```


## serdp_edna_collection
```{r}

collection_serdp_edna <- full_serdp_edna %>%
  clean_names() %>% 
  unite(site_code, state:site_number,  sep = "", na.rm = T, remove = F) %>% 
  mutate(site_code = str_to_lower(site_code),
         date_collected = format_iso_8601(parse_date(date_collected)),
         ext_date = format_iso_8601(parse_date(ext_date)),
         date_ran = format_iso_8601(parse_date(date_ran))) %>% 
  mutate(region = case_when(state == "PA" ~ "pennsylvania",
                           state == "NM" ~ "new_mexico",
                           state == "LA" ~ "louisiana",
                           state == "TN" ~ "tennessee",
                           state == "VT" ~ "vermont"),
         control = case_when(control_experimental == "C" ~ 1,
                             control_experimental == "E" ~ 0)) %>% 
  select(!c(state, site_number)) %>% 
  group_by(site_code, date_collected) %>% 
  mutate(temp_id = cur_group_id()) %>% 
  filter(!duplicated(temp_id)) %>% 
  select(!c(temp_id, year, month, control_experimental)) %>% 
  relocate(control, .after = number_filters) %>% 
  mutate(sample_pass_fail = case_when(sample_pass_fail == "P" ~ 1,
                                      sample_pass_fail == "F, neg ext control had Bd" ~ 0),
         bd_pos_neg = case_when(bd_pos_neg == "N" ~ 0,
                                bd_pos_neg == "P" ~ 1),
         bsal_pos_neg = case_when(bsal_pos_neg == "N" ~ 0,
                                  bsal_pos_neg == "N;N;N" ~ 0),
         q_pcr_neg_control = case_when(q_pcr_neg_control == "Neg" ~ 1),
         sample_rerun = str_to_upper(sample_rerun),
         resus_vol = str_replace_all(resus_vol, "\\*", ""))  %>% 
  rename(sample_pass = sample_pass_fail,
         bd_positive = bd_pos_neg,
         bsal_positive = bsal_pos_neg,
         qpcr_neg_control_pass = q_pcr_neg_control,
         edna_comments = notes) %>% 
  mutate(serdp_bd_id = UUIDgenerate(output = "uuid", n = n()),
         visit_id = as.UUID(""))

write_csv(collection_serdp_edna, here("clean_tables", "edna_serdp_bd.csv"))

```


# panama edna - ONLY HALF OF 2022 DATA

## full panama edna data
```{r}
pan_site_edna2022 <- read_csv(here("data", "panama_legacy", "pan_site_edna22.csv")) %>% 
  clean_names() %>% 
  select(fulcrum_id, region, site, start_date)

pan_edna_22 <- read_csv(here("data", "panama_legacy", "pan_edna_22.csv")) %>% 
  clean_names() %>% 
  select(fulcrum_parent_id, geometry, id_edna_sample:notes_of_edna_sample)

full_pan_edna <- left_join(pan_site_edna2022, pan_edna_22, by = (c( "fulcrum_id" = "fulcrum_parent_id")))
```

## panama edna site table
```{r}
  
pan_sites_edna <- full_pan_edna %>% 
  select(region, site, start_date) %>% 
  mutate(region = str_replace_all(str_to_lower(region), " ", "_"),
         site = str_replace_all(str_to_lower(site), " ", "_"),
         start_date = format_iso_8601(parse_date(start_date))) %>% 
  rename(date_collected = start_date) %>% 
  group_by(site) %>% 
  mutate(temp_id = cur_group_id()) %>% 
  filter(!duplicated(temp_id)) %>% 
  select(!c(temp_id))

```

## panama date table
```{r}

pan_date_table <- full_pan_edna %>% 
  select(site, start_date) %>% 
  mutate(site = str_replace_all(str_to_lower(site), " ", "_"),
         start_date = format_iso_8601(parse_date(start_date)),
         year = year(start_date),
         month = month(start_date),
         day = day(start_date))%>% 
  rename(date_collected = start_date) %>% 
  group_by(site, date_collected) %>% 
  mutate(temp_id = cur_group_id()) %>% 
  filter(!duplicated(temp_id)) %>% 
  select(!c(temp_id))


```


## pan edna metadata
```{r}

pan_edna_metadata <- full_pan_edna %>% 
    mutate(region = str_replace_all(str_to_lower(region), " ", "_"),
         site = str_replace_all(str_to_lower(site), " ", "_"),
         start_date = format_iso_8601(parse_date(start_date))) %>% 
  select(!c(fulcrum_id)) %>% 
  drop_na(geometry) %>% 
  rename(edna_comments = notes_of_edna_sample) %>% 
  mutate(control = if_else(is.na(start_time_negative_control_edna_filtering), 0, 1)) %>% 
  unite(filter_start_time, c(start_time_negative_control_edna_filtering, start_time_sample_edna_filtering), na.rm = T) %>% 
  unite(filter_end_time, c(finish_time_negative_control_edna_filtering, finish_time_sample_edna_filtering), na.rm = T) %>% 
   relocate(control, .after=id_edna_sample)%>% 
  rename(date_collected = start_date,
         edna_location_m = transect_meters_sampled_m,
         edna_volume_ml = volume_of_filtered_sample_ml,
         edna_sample_id = id_edna_sample) %>% 
  mutate(geometry = str_remove(geometry, "POINT "),
         geometry = str_remove_all(geometry, "[()]"),
         geometry = str_replace(geometry, " ", ","),
         active_passive = "active",
         filter_size_um = "",
         edna_volume_ml = if_else(is.na(edna_volume_ml), 1000, edna_volume_ml))


filt_dups <- pan_edna_metadata %>% 
  filter(edna_sample_id %in% c("220721_edna_001", "220721_edna_002", "220721_edna_003",
                               "220721_edna_004", "220721_edna_007", "220721_005", "220721_006",
                               "220721_007", "220723_001",
                               "220723_002", "220723_003", "220724_001", "220724_002", "220724_003",
                               "220726_eDNA_001", "220726_eDNA_002", "220726_eDNA_003",
                               "220729_eDNA_001", "220729_eDNA_002", "220729_eDNA_003",
                               "220729_eDNA_004", "220729_eDNA_005"))
samps_0.45 <- filt_dups %>% 
  mutate(filter_size_um = "0.45")

samps_5 <- filt_dups %>% 
  mutate(filter_size_um = "5")

double_samps <- rbind(samps_0.45, samps_5) 

single_samps <- pan_edna_metadata %>% 
  filter(!edna_sample_id %in% c(double_samps$edna_sample_id)) %>% 
  mutate(filter_size_um = case_when(edna_sample_id == "220728_eDNA_001" ~ "5",
                                    edna_sample_id == "220728_eDNA_002" ~ "0.45",
                                    edna_sample_id == "220728_eDNA_003" ~ "5",
                                    edna_sample_id == "220728_eDNA_004" ~ "0.45",
                                    edna_sample_id == "220728_eDNA_005" ~ "5",
                                    edna_sample_id == "220728_eDNA_006" ~ "0.45"))

pan_edna_metadata <- rbind(double_samps, single_samps)


write_csv(pan_edna_metadata, here("clean_tables", "edna_panama_survey.csv"))  

```

# SN edna data
## db connection
```{r}

tryCatch({
print("Connecting to Database…")
connection <- dbConnect(drv = dbDriver("Postgres"),
                        dbname = Sys.getenv("sn_dbname"),
                        host = Sys.getenv("sn_host"),
                        port = Sys.getenv("sn_port"),
                        user = Sys.getenv("sn_user"),
                        password = Sys.getenv("sn_password"),
                        timezone=NULL)
print("Database Connected!")
},
error=function(cond) {
print("Unable to connect to Database.")})
# set search path for 'survey_data' schema
dbSendQuery(connection, "set search_path = 'public'")

```
```{sql, connection = connection, output.var = sn_edna_sites}

select s.*, v.*, s2.*
from site s
join visit v on s.id = v.site_id 
join survey s2 on v.id = s2.visit_id
where v.visit_date = '2022-09-14';

```

```{sql, connection = connection, output.var = sing_sn_site}

select s. *
from site s
where s.id = '72336';

```

## bind sn sites
```{r}

sn_sites <- plyr::rbind.fill(sn_edna_sites, sing_sn_site) %>% 
  select(!c(site_id)) %>% 
  mutate(visit_date = if_else(is.na(visit_date), as.character("2022-09-14"), as.character(visit_date)),
         visit_status = if_else(is.na(visit_status), as.character("suitable"), as.character(visit_status)),
         id..18 = if_else(is.na(id..18), "c364972d-a339-4aab-ab28-b49f88a5d5dc", id..18))
  

```

## load edna metadata from fulcrum
```{r}

sn_edna_meta <- read_csv(here("data", "sn", "edna", "edna_sn_2022.csv")) %>% 
  select(!c(fulcrum_id, fulcrum_record_id, version, created_at, updated_at, created_by,
            updated_by, latitude, longitude, geometry))



```
## join all sn edna together - NEED to MOVE Data manually for site 72336 ID = c364972d-a339-4aab-ab28-b49f88a5d5dc

```{r}

sn_edna <- sn_sites %>% 
  left_join(sn_edna_meta, by = c("id..18" ="fulcrum_parent_id")) %>% 
  mutate(location = "usa",
         region = "california",
         year = year(visit_date),
         month = month(visit_date),
         day = day(visit_date)) %>% 
  select(!c(name, id..13, id..18, survey_type, visit_id)) %>% 
  rename(site = id)

```

## pull SN site data
```{r}

sn_site <- sn_edna %>% 
  select(region, c(1:11)) %>% 
  group_by(site) %>% 
  unique() %>% 
  mutate(utm_zone = 11) %>% 
  select(!c(drainage, county, topo, jurisdiction))

```

## pull out sn visit data
```{r}

sn_visit <- sn_edna %>% 
  select(site, c(12:14), year, month, day) %>% 
  group_by(site, visit_date) %>% 
  unique() %>% 
  rename(date_collected = visit_date)

```

## pull out sn survey data
```{r}

sn_survey <- sn_edna %>% 
  select(site, visit_date, wind, sky, collect_time, c(edna_filter_id:edna_sample_comment), region) %>% 
  select(!c(frozen_hrs, sample_processing)) %>% 
  rename(edna_sample_id = edna_filter_id,
         edna_comments = edna_sample_comment, 
         filter_start_time = start_time_edna,
         filter_end_time = end_time_edna,
         edna_volume_ml = edna_volume,
         edna_location_m = location_edna,
         date_collected = visit_date,
         filter_size_um = filter_size) %>% 
  mutate(edna_comments = str_to_lower(edna_comments),
         control = if_else(str_detect(edna_sample_id, "Negative"), 1, 0) | 
         if_else(str_detect(edna_comments, "negative"), 1, 0),
         control = if_else(is.na(control), "FALSE", as.character(control)),
         control = if_else(control == "TRUE", 1, 0),
         active_passive = if_else(is.na(active_passive), "active", active_passive))
  

```



# bind site tables 
```{r}

edna_sites <- plyr::rbind.fill(pan_sites_edna, serdp_edna_sitetable, sn_site)%>% 
  mutate(site = if_else(is.na(site), site_code, site)) %>% 
  group_by(site) %>% 
  mutate(site_id = UUIDgenerate(output = c("uuid")),
         region_id = as.UUID(""))

write_csv(edna_sites, here("clean_tables", "edna_site.csv"))

```

# bind date/visit table
```{r}

visit_table <- plyr::rbind.fill(pan_date_table, serdp_edna_visit_table, sn_visit) %>% 
  rename(visit_comment = comment) %>% 
  group_by(site, date_collected) %>% 
  mutate(visit_id = UUIDgenerate(output = c("uuid")),
         site_id = as.UUID(""),
         site = if_else(is.na(site), site_code, site))

write_csv(visit_table, here("clean_tables", "edna_visit.csv"))

```

# bind sn and pan edna data
```{r}

edna_survey_table <- plyr::rbind.fill(pan_edna_metadata, sn_survey) %>% 
  mutate(survey_id = UUIDgenerate(output = "uuid", n = n()),
         visit_id = as.UUID("")) %>% 
  rename(survey_comments = edna_comments)

write_csv(edna_survey_table, here("clean_tables", "edna_survey.csv"))

```

