---
title: "penn_2023_append"
format: html
editor: source
---

## Load Packages

```{r}
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}

# librarian downloads, if not already downloaded, and reads in needed packages
librarian::shelf(tidyverse, here, janitor, lubridate, RPostgres, stringr, DBI, parsedate, uuid, hms)
```

## Load CSV Exports and Trim Fat

```{r}
#| message: false

survey_info <- read_csv(here("data", "new_2023_data", "penn", "exp_full_season",
                             "1_penn_surveyinformation", "1_penn_surveyinformation.csv")) %>% 
  select(!c(2:14)) %>% 
  clean_names()

survey_acoustic <- read_csv(here("data", "new_2023_data", "penn", "exp_full_season",
                             "2_penn_acousticsurvey", "2_penn_acousticsurvey.csv")) %>% 
  select(!c(2:14)) %>% 
  clean_names() %>% 
  mutate(detection_type = "aural")

acoustic_obs <- read_csv(here("data", "new_2023_data", "penn", "exp_full_season",
                             "2_penn_acousticsurvey", "2_penn_acousticsurvey_acoustic_survey.csv")) %>% 
  select(!c(4:11)) %>% 
  clean_names()%>% 
  mutate(detection_type = "aural")


survey_edna <- read_csv(here("data", "new_2023_data", "penn", "exp_full_season", "3_penn_ednasurvey",
                             "3_penn_ednasurvey.csv")) %>% 
  select(!c(2:14)) %>% 
  clean_names()


edna_obs_col <- read_csv(here("data", "new_2023_data", "penn", "exp_full_season", "3_penn_ednasurvey",
                          "3_penn_ednasurvey_edna_collection.csv")) %>% 
  select(!c(4:11)) %>% 
  clean_names()


edna_obs_filt <- read_csv(here("data", "new_2023_data", "penn", "exp_full_season",
                               "3_penn_ednasurvey",
                               "3_penn_ednasurvey_edna_collection_edna_filtering.csv")) %>% 
  select(!c(4:11)) %>% 
  clean_names()

survey_ves <- read_csv(here("data", "new_2023_data", "penn", "exp_full_season",
                            "4_penn_visualencountersurvey", "4_penn_visualencountersurvey.csv")) %>% 
  select(!c(2:14)) %>% 
  clean_names()%>% 
  mutate(detection_type = "visual")

ves_obs <- read_csv(here("data", "new_2023_data", "penn", "exp_full_season",
                            "4_penn_visualencountersurvey", 
                         "4_penn_visualencountersurvey_visual_encounter_information.csv")) %>% 
  select(!c(4:11)) %>% 
  clean_names()%>% 
  mutate(detection_type = "visual")

survey_capture <- read_csv(here("data", "new_2023_data", "penn", "exp_full_season", 
                                "5_penn_capturesurvey", "5_penn_capturesurvey.csv")) %>% 
  select(!c(2:14)) %>% 
  clean_names()%>% 
  mutate(detection_type = "capture")

capture_obs <- read_csv(here("data", "new_2023_data", "penn", "exp_full_season", 
                                "5_penn_capturesurvey", 
                             "5_penn_capturesurvey_captured_amphibian_information.csv")) %>% 
  select(!c(4:12)) %>% 
  clean_names()%>% 
  mutate(detection_type = "capture")

samp_proces <- read_csv(here("data", "new_2023_data", "penn", "exp_full_season",
                             "6_penn_sampleprocessing",
                             "6_penn_sampleprocessing.csv")) %>% 
  select(!c(2:14)) %>% 
  clean_names()

samp_procces_obs <- read_csv(here("data", "new_2023_data", "penn", "exp_full_season",
                             "6_penn_sampleprocessing",
                             "6_penn_sampleprocessing_amphibian_capture_survey_collections.csv"))%>% 
  select(!c(4:11)) %>% 
  clean_names()

cmr <- read_csv(here("data", "new_2023_data", "penn", "exp_full_season", "supp_penn_cmrids",
                     "supp_penn_cmrids.csv")) %>% 
  select(!c(2:14)) %>% 
  clean_names()

```

## DB Connection

```{r}
tryCatch({
    drv <- dbDriver("Postgres")
    print("Connecting to Database…")
    connection <- dbConnect(drv,
                 dbname = Sys.getenv("aws_dbname"),
                 host = Sys.getenv("aws_host"),
                 port = Sys.getenv("aws_port"),
                 user = Sys.getenv("aws_user"),
                 password = Sys.getenv("aws_password"),
                 timezone=NULL)
    print("Database Connected!")
    },
    error=function(cond) {
            print("Unable to connect to Database.")
    })

dbExecute(connection, "set search_path to survey_data")
```

## Merge unique visits include site

### Merge all 2023 visits

```{r}

comms <- survey_info %>% 
  select(site, sampling_event_comments, date)

unique_visits <- plyr::rbind.fill(survey_acoustic, survey_capture, survey_edna, survey_info, survey_ves) %>% 
  select(date, site, survey_time) %>% 
  group_by(date, site, survey_time) %>% 
  mutate(temp_id = cur_group_id()) %>% 
  filter(!duplicated(temp_id)) %>% 
  left_join(comms, by = c("site", "date")) %>% 
  select(!temp_id) %>% 
  rename(visit_comments = sampling_event_comments) %>% 
  mutate(site = str_to_lower(site),
         site = str_replace_all(site, "-", "_"),
         site = str_replace_all(site, " ", "_"),
         survey_time = str_to_lower(survey_time))

```

### Pull site f.key

```{r}

s.fkey_q <- "select site, site_id
            from site;"

s.key <- dbGetQuery(connection, s.fkey_q)

```

### populate site k.key on visit table

```{r}

unique_visits_fkey <- unique_visits %>% 
  inner_join(s.key, by = c("site")) %>% 
  mutate(visit_id = UUIDgenerate()) %>% 
  ungroup()


```

### final site tabe

```{r}

fin_visit <- unique_visits_fkey %>% 
  ungroup() %>% 
  select(!c(site))



dbAppendTable(connection, "visit", fin_visit)
  

```

## Survey data include date and survey_time

### Merge all survey data

```{r}

mid_surv_cap <- survey_info %>% 
  select(!c(fulcrum_id, site_other, start_time, end_time, survey_time)) %>% 
  mutate(detection_type = "capture")

mid_surv_ves <- survey_info %>% 
  select(!c(fulcrum_id, site_other, start_time, end_time, survey_time)) %>% 
  mutate(detection_type = "visual")

mid_surv_aural <- survey_info%>% 
  select(!c(fulcrum_id, site_other, start_time, end_time, survey_time)) %>% 
  mutate(detection_type = "aural")

surv_info <- plyr::rbind.fill(mid_surv_cap, mid_surv_ves, mid_surv_aural)


mid_unique_survey <- plyr::rbind.fill(survey_acoustic, survey_capture, survey_ves) %>% 
  select(!c(fulcrum_id, observer, observer_other, acoustic_survey_comments)) %>% 
  full_join(surv_info, by = c("site", "date", "detection_type")) %>% 
  select(!c(site_other))

unique_survey <- mid_unique_survey %>% 
  group_by(site, date, detection_type) %>% 
  mutate(start_time = as_hms(mean(start_time)),
         end_time = as_hms(mean(end_time))) %>% 
  select(!c(air_temperature_measurement_time,
            water_temperature_measurement_time, conductivity_us)) %>% 
  unite(survey_comments, c("survey_comments", "survey_description", "sampling_event_comments"), na.rm = T,
        sep = ",") %>% 
  unite(observers, c("observers", "other_observers"), na.rm = T, sep = ",") %>% 
  rename(wind = wind_conditions,
         sky = sky_conditions,
         relative_humidity_percent = humidity,
         pressure_psi = pressure, # need to confirm units
         wind_speed_m_s = wind_speed_ms,
         air_temp_c = air_temperature_c,
         dissolved_o2_percent = dissolved_oxygen,
         tds_ppm = total_dissolved_solids, # need to confirm units
         water_temp_c = water_temperature_c,
         p_h = ph) %>% 
  mutate(survey_time = str_to_lower(survey_time),
         site = str_to_lower(str_replace_all(site, "-", "_")),
         site = str_replace_all(site, " ", "_")) %>% 
  mutate(temp_id = cur_group_id(),
         survey_time = if_else(is.na(survey_time), "night", survey_time)) %>% 
  filter(!duplicated(temp_id)) %>% 
  select(!temp_id)


```

### Pull visit pkey from unique table above

```{r}

surv_fkey <- unique_visits_fkey %>% 
  select(date, visit_id, site)


```

### Join visit pkey into surv fkey

```{r}

unique_survey_fkey <- unique_survey %>% 
  left_join(surv_fkey, by = c("date", "site")) %>% 
  mutate(p_h = if_else(p_h == 0.00, NA, p_h)) %>% 
  group_by(site, date, detection_type) %>% 
  mutate(survey_id = UUIDgenerate(output = c("uuid"))) %>% 
  filter(!duplicated(survey_id)) %>% 
  mutate(duration_min = if_else(end_time < start_time,
                            as_hms(86400) - start_time + end_time,
                            end_time - start_time),
         duration_min = duration_min/60,
         duration_min = str_remove(duration_min, " secs"),
         duration_min  = round(as.numeric(duration_min), 2))

```

### final survey table

```{r}

fin_survey <- unique_survey_fkey %>% 
  ungroup() %>% 
  select(!c(date, survey_time, site)) %>% 
  rename(observer = observers,
         duration_minutes = duration_min) %>% 
  mutate(duration_minutes = as.integer(duration_minutes))

dbAppendTable(connection, "survey", fin_survey)

```

## Capture table

### merge and clean capture tables

```{r}
#cap_col <- read_csv(here("clean_tables", "capture.csv"))


mid_cap <- survey_info %>% 
  left_join(survey_capture, by = c("site" , "date")) %>% 
  select(fulcrum_id.y, detection_type, date, site, survey_time.x) %>% 
  rename(fulcrum_id = fulcrum_id.y,
         survey_time = survey_time.x) %>% 
  left_join(capture_obs, by = c("fulcrum_id" = "fulcrum_parent_id")) %>% 
  select(detection_type.x, date, site, survey_time, detection_type.x, body_temperature, bag_id, species_capture, 
         time_of_capture, microhabitat_type, microhabitat_wet, microhabitat_temperature, amphibian_comments)

mid_samp_proc <- samp_proces %>% 
  left_join(samp_procces_obs, by= c("fulcrum_id" = "fulcrum_parent_id")) %>% 
  select(!c(fulcrum_id, fulcrum_id.y, fulcrum_record_id, c(norep_bathvolume_50ml_acid_05ml:ul_of_norep_01688mgml),
            c(photo:photo_url), c(amp_ig_ne_injected:amp_ig_comments)))

neg_controls <- mid_samp_proc %>% 
  filter(species_capture == "Negative Control") %>% 
  select(!c(processor_other, sex_other, survey_comments, life_stage_other)) %>% 
  select(!c(species_capture_other:body_mass)) %>% 
  rename(site = location) %>% 
  mutate(species_capture = str_to_lower(str_replace_all(species_capture, " ", "_")),
         survey_time = str_to_lower(survey_time),
         site = str_to_lower(str_replace_all(site, " ", "_")))

mid_samp_proc <- mid_samp_proc %>% 
  filter(!species_capture == "Negative Control") %>% 
  select(!species_capture_other)

unique_cap <- mid_samp_proc %>% 
  left_join(mid_cap, by = c("location"= "site", "date", "bag_id")) %>% 
  select(!c(survey_time.y, species_capture.y, life_stage_other, sex_other,
            survey_comments)) %>% 
  rename(detection_type = detection_type.x,
         survey_time = survey_time.x,
         species_capture = species_capture.x,
         site = location) %>% 
  unite(processor, c("processor", "processor_other"), na.rm = T, sep = "") %>% 
  mutate(site = str_to_lower(str_replace_all(site, "-", "_")),
         site = str_replace_all(site, " ", "_"),
         species_capture = str_to_lower(str_replace_all(species_capture, " ", "_")),
         survey_time = str_to_lower(survey_time)) %>% 
  unite(capture_comments, c("amphibian_comments", "capture_comments"), na.rm = T,
        sep = ", ") %>% 
  rename(body_temp_c = body_temperature,
         svl_mm = snout_vent_length,
         body_and_bag_mass_g = body_and_bag_mass,
         bag_mass_g = bag_mass,
         body_mass_g = body_mass) %>% 
  ungroup() %>% 
  mutate(amp_id = if_else(capture_mark_recapture %in% ("cf358e11-d6da-4637-af56-c384d683e6fb"), "Pe_AMP00000", amp_id)) %>% 
  plyr::rbind.fill(neg_controls)



```

### populate survey fkey

```{r}

cap_fkey <- unique_survey_fkey %>% 
  select(site, date, detection_type, survey_time, survey_id)


unique_cap_fkey <- unique_cap %>% 
  mutate(detection_type = "capture",
         capture_id = UUIDgenerate(n = n())) %>% 
  left_join(cap_fkey, by = c("site", "date", "detection_type", "survey_time"))
  

```

### final capture table

#### empty column search

## create empty columns in DB which are new to this data set

```{r}

final_cap <- unique_cap_fkey %>% 
  select(!c(survey_time, detection_type, site, date)) %>% 
  rename(microbiome_swab_id = microbiome_id,
         sierra_bd_swab_id = bd_swab_id_sv) %>% 
  mutate(sex = str_to_lower(sex),
         capture_type = str_to_lower(capture_type),
         life_stage = str_to_lower(life_stage))


q_col <- "SELECT *
          FROM capture
          LIMIT 1;"

col_names <- dbGetQuery(connection, q_col) %>%
  colnames()

db_cols <- final_cap %>%
  colnames()

missing_cols <- setdiff(db_cols, col_names) %>%
  print() %>%
  as.character()


add_col_q <- paste0("alter table capture
                  add ", missing_cols[1]," varchar;")

dbExecute(connection, add_col_q)

add_col_q <- paste0("alter table capture
                  add ", missing_cols[2]," varchar;")

dbExecute(connection, add_col_q)



dbAppendTable(connection, "capture", final_cap)

```

## VES

### clean and merged ves data

```{r}

ves_c <- read_csv(here("clean_tables", "ves.csv"))

mid_ves <- survey_ves %>% 
  left_join(ves_obs, by = c("fulcrum_id" = "fulcrum_parent_id")) %>% 
  select(!c(fulcrum_id, detection_type.x, fulcrum_id.y, fulcrum_record_id, start_time, end_time,
            survey_description)) %>% 
  rename(detection_type = detection_type.y)


unique_ves <- mid_ves %>% 
  unite(observer, c("observer", "observer_other"), na.rm = T, sep = "") %>% 
  unite(species_ves, c("species_ves", "species_ves_other"), na.rm = T, sep = "") %>% 
  mutate(site = str_to_lower(str_replace_all(site, " ", "_")),
         site = str_replace_all(site, "-", "_"),
         survey_time = str_to_lower(survey_time),
         species_ves = str_to_lower(str_replace_all(species_ves, " ", "_"))) %>% 
  rename(ves_comments = comments_ves,
         count = count_ves)


```

### populate VES fkey

```{r}

ves_fkey <- unique_survey_fkey %>% 
  select(site, date, detection_type, survey_time, survey_id)

unique_ves_fkey <- unique_ves %>% 
  left_join(ves_fkey, by = c("site", "date", "detection_type", "survey_time")) %>% 
  mutate(ves_id = UUIDgenerate(n = n()))



```

### final ves table

```{r}

final_ves <- unique_ves_fkey %>% 
  select(!c(site, date, survey_time, detection_type))

dbAppendTable(connection, "ves", final_ves)

```

## aural

### clean and merge arual

```{r}

aural_cols <- read_csv(here("clean_tables", "aural.csv"))


mid_aural <- survey_acoustic %>% 
  left_join(acoustic_obs, by = c("fulcrum_id" = "fulcrum_parent_id"))%>% 
  select(!c(fulcrum_id, detection_type.x, fulcrum_id.y, fulcrum_record_id, start_time, end_time,
            observer_other, species_acoustic_other, acoustic_survey_comments))

unique_aural <- mid_aural %>% 
  rename(detection_type = detection_type.y) %>% 
  mutate(site = str_to_lower(str_replace_all(site, " ", "_")),
         site = str_replace_all(site, "-", "_"),
         species_acoustic = str_to_lower(str_replace_all(species_acoustic, " ", "_")),
         survey_time = str_to_lower(survey_time)) %>% 
  rename(species_aural = species_acoustic,
         aural_comments = acoustic_species_comments)
  


```

### populate aural fkey

```{r}

aural_fkey <- unique_survey_fkey %>% 
  select(site, date, detection_type, survey_time, survey_id)


unique_aural_fkey <- unique_aural %>% 
  mutate(detection_type = "aural",
         aural_id = UUIDgenerate(n = n())) %>% 
  left_join(aural_fkey, by = c("site", "date", "detection_type", "survey_time"))
  

```

### final aural table

```{r}

final_aural <- unique_aural_fkey %>% 
  select(!c(site, date, detection_type, survey_time))

dbAppendTable(connection, "aural", final_aural)

```

## CMR table

```{r}

cmr_cols <- read_csv(here("clean_tables", "penn_cmr.csv"))

final_cmr <- cmr %>% 
  select(!c(species_other, location, species)) %>% 
  unite(cmr, c("cmr_id", "cmr_id_other"), na.rm = T, sep = "") %>% 
  rename(capture_mark_recapture = fulcrum_id,
         cmr_id = cmr)

dbAppendTable(connection, "cmr", final_cmr)

```
