---
title: "penn_2023_append"
format: html
editor: visual
---

## Load Packages

```{r}
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}

# librarian downloads, if not already downloaded, and reads in needed packages
librarian::shelf(tidyverse, here, janitor, lubridate, RPostgres, stringr, DBI, parsedate, uuid, hms)
```

## Load CSV Exports and Trim Fat

```{r}

survey_info <- read_csv(here("data", "new_2023_data", "penn", "exp_06_12_23",
                             "1_penn_surveyinformation", "1_penn_surveyinformation.csv")) %>% 
  select(!c(2:14)) %>% 
  clean_names()

survey_acoustic <- read_csv(here("data", "new_2023_data", "penn", "exp_06_12_23",
                             "2_penn_acousticsurvey", "2_penn_acousticsurvey.csv")) %>% 
  select(!c(2:14)) %>% 
  clean_names() %>% 
  mutate(detection_type = "aural")

acoustic_obs <- read_csv(here("data", "new_2023_data", "penn", "exp_06_12_23",
                             "2_penn_acousticsurvey", "2_penn_acousticsurvey_acoustic_survey.csv")) %>% 
  select(!c(4:11)) %>% 
  clean_names()%>% 
  mutate(detection_type = "aural")


survey_edna <- read_csv(here("data", "new_2023_data", "penn", "exp_06_12_23", "3_penn_ednasurvey",
                             "3_penn_ednasurvey.csv")) %>% 
  select(!c(2:14)) %>% 
  clean_names()


edna_obs_col <- read_csv(here("data", "new_2023_data", "penn", "exp_06_12_23", "3_penn_ednasurvey",
                          "3_penn_ednasurvey_edna_collection.csv")) %>% 
  select(!c(4:11)) %>% 
  clean_names()


edna_obs_filt <- read_csv(here("data", "new_2023_data", "penn", "exp_06_12_23",
                               "3_penn_ednasurvey",
                               "3_penn_ednasurvey_edna_collection_edna_filtering.csv")) %>% 
  select(!c(4:11)) %>% 
  clean_names()

survey_ves <- read_csv(here("data", "new_2023_data", "penn", "exp_06_12_23",
                            "4_penn_visualencountersurvey", "4_penn_visualencountersurvey.csv")) %>% 
  select(!c(2:14)) %>% 
  clean_names()%>% 
  mutate(detection_type = "visual")

ves_obs <- read_csv(here("data", "new_2023_data", "penn", "exp_06_12_23",
                            "4_penn_visualencountersurvey", 
                         "4_penn_visualencountersurvey_visual_encounter_information.csv")) %>% 
  select(!c(4:11)) %>% 
  clean_names()%>% 
  mutate(detection_type = "visual")

survey_capture <- read_csv(here("data", "new_2023_data", "penn", "exp_06_12_23", 
                                "5_penn_capturesurvey", "5_penn_capturesurvey.csv")) %>% 
  select(!c(2:14)) %>% 
  clean_names()%>% 
  mutate(detection_type = "capture")

capture_obs <- read_csv(here("data", "new_2023_data", "penn", "exp_06_12_23", 
                                "5_penn_capturesurvey", 
                             "5_penn_capturesurvey_captured_amphibian_information.csv")) %>% 
  select(!c(4:12)) %>% 
  clean_names()%>% 
  mutate(detection_type = "capture")

samp_proces <- read_csv(here("data", "new_2023_data", "penn", "exp_06_12_23",
                             "6_penn_sampleprocessing",
                             "6_penn_sampleprocessing.csv")) %>% 
  select(!c(2:14)) %>% 
  clean_names()

samp_procces_obs <- read_csv(here("data", "new_2023_data", "penn", "exp_06_12_23",
                             "6_penn_sampleprocessing",
                             "6_penn_sampleprocessing_amphibian_capture_survey_collections.csv"))%>% 
  select(!c(4:11)) %>% 
  clean_names()

cmr <- read_csv(here("data", "new_2023_data", "penn", "exp_06_12_23", "supp_penn_cmrids",
                     "supp_penn_cmrids.csv")) %>% 
  select(!c(2:14)) %>% 
  clean_names()

```

## DB Connection

```{r}
tryCatch({
    drv <- dbDriver("Postgres")
    print("Connecting to Database…")
    connection <- dbConnect(drv,
                 dbname = Sys.getenv("aws_dbname"),
                 host = Sys.getenv("aws_host"),
                 port = Sys.getenv("aws_port"),
                 user = Sys.getenv("aws_user"),
                 password = Sys.getenv("aws_password"),
                 timezone=NULL)
    print("Database Connected!")
    },
    error=function(cond) {
            print("Unable to connect to Database.")
    })

dbExecute(connection, "set search_path to survey_data")
```

## Merge unique visits include site

### Merge all 2023 visits

```{r}

comms <- survey_info %>% 
  select(site, sampling_event_comments, date)

unique_visits <- plyr::rbind.fill(survey_acoustic, survey_capture, survey_edna, survey_info, survey_ves) %>% 
  select(date, site, survey_time) %>% 
  group_by(date, site) %>% 
  mutate(temp_id = cur_group_id()) %>% 
  filter(!duplicated(temp_id)) %>% 
  left_join(comms, by = c("site", "date")) %>% 
  select(!temp_id) %>% 
  rename(visit_comments = sampling_event_comments) %>% 
  mutate(site = str_to_lower(site),
         site = str_replace_all(site, "-", "_"),
         site = str_replace_all(site, " ", "_"),
         survey_time = str_to_lower(survey_time))

```

### Pull site f.key

```{r}

s.fkey_q <- "select site, site_id
            from site;"

s.key <- dbGetQuery(connection, s.fkey_q)

```

### populate site k.key on visit table - READY

```{r}

unique_visits_fkey <- unique_visits %>% 
  inner_join(s.key, by = c("site")) %>% 
  mutate(visit_id = UUIDgenerate())


```

## Survey data include date and survey_time

### Merge all survey data

```{r}

mid_surv_cap <- survey_info %>% 
  select(!c(fulcrum_id, site_other, start_time, end_time, survey_time)) %>% 
  mutate(detection_type = "capture")

mid_surv_ves <- survey_info %>% 
  select(!c(fulcrum_id, site_other, start_time, end_time, survey_time)) %>% 
  mutate(detection_type = "visual")

mid_surv_aural <- survey_info%>% 
  select(!c(fulcrum_id, site_other, start_time, end_time, survey_time)) %>% 
  mutate(detection_type = "aural")

surv_info <- plyr::rbind.fill(mid_surv_cap, mid_surv_ves, mid_surv_aural)


mid_unique_survey <- plyr::rbind.fill(survey_acoustic, survey_capture, survey_ves) %>% 
  select(!c(fulcrum_id, observer, observer_other, acoustic_survey_comments)) %>% 
  left_join(surv_info, by = c("site", "date", "detection_type"))

unique_survey <- mid_unique_survey %>% 
  group_by(site, date, detection_type) %>% 
  mutate(start_time = as_hms(mean(start_time)),
         end_time = as_hms(mean(end_time))) %>% 
  select(!c(air_temperature_measurement_time,
            water_temperature_measurement_time, conductivity_us)) %>% 
  unite(survey_comments, c("survey_comments", "survey_description", "sampling_event_comments"), na.rm = T,
        sep = ",") %>% 
  unite(observers, c("observers", "other_observers"), na.rm = T, sep = ",") %>% 
  rename(wind = wind_conditions,
         sky = sky_conditions,
         relative_humidity_percent = humidity,
         pressure_psi = pressure, # need to confirm units
         wind_speed_m_s = wind_speed_ms,
         air_temp_c = air_temperature_c,
         dissolved_o2_percent = dissolved_oxygen,
         tds_ppm = total_dissolved_solids, # need to confirm units
         water_temp_c = water_temperature_c,
         p_h = ph) %>% 
  mutate(survey_time = str_to_lower(survey_time),
         site = str_to_lower(str_replace_all(site, "-", "_")),
         site = str_replace_all(site, " ", "_"))


```

### Pull visit pkey from unique table above

```{r}

surv_fkey <- unique_visits_fkey %>% 
  select(date, visit_id, site)


```

### Join visit pkey into surv fkey - Not fully unique due to multiple users per survey....

```{r}

unique_survey_fkey <- unique_survey %>% 
  left_join(surv_fkey, by = c("date", "site")) %>% 
  mutate(p_h = if_else(p_h == 0.00, NA, p_h)) %>% 
  group_by(site, date, detection_type) %>% 
  mutate(survey_id = UUIDgenerate(output = c("uuid"))) %>% 
  filter(!duplicated(survey_id)) %>% 
  mutate(duration_min = if_else(end_time < start_time,
                            as_hms(86400) - start_time + end_time,
                            end_time - start_time),
         duration_min = duration_min/60)

unique_survey_fkey$duration_min <- str_sub(unique_survey_fkey$duration_min, -4) %>% 
  as.numeric()

```

## Prep capture table

```{r}

mid_cap <- capture_obs %>% 
  left_join(samp_proces, by = c("location", "date", "bag_id"))

```
